A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-19 rmtw/a6/latex8.tex
asdda

\section{Related Work}

@@

\Section{Acknowledgement}

>>>>

\section{Related Work}
Our work is mainly related to the research area of APIs. This discipline will be discussed in both section 2.1 and 2.2. Our research is directly related to the fields of software evolution and software ecosystems. Section 2.2 will describe APIs in the context of those two fields.

@@

\Section{Acknowledgement}
John had the main responsibility for sections 1, 2. William had the main responsibility for section 3. Section 3.6 and the interview questions were written together. We have, however, worked on all sections jointly and all sections have been reviewed by both William and John.
